### 2017-10-13 Gruba/02-overview.tex

%The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
By Definition \textit{\ref{def:blog}} and \textit{\ref{def:user}}, $u = M_b.O$ and $M_b \in B_u$.

@@

\subsection{\sys{} Framework}
System \sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media.
Figure \ref{fig:framework} shows the architectural components of \sys{}. %, mainly comprising Sina Microblog Data, Key Modules and Profile Demonstrator.

@@

	\stab(1)  Feature Extraction: By coalescing the microblog data, each user is depicted by a bunch of features, which are grouped into three categories. They are features of \textit{Basics} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., the long-term/recent interests, as well as the explicit/implicit interests). These features are extracted from the stored  Sina Weibo data by Feature Extraction module, and serve as the input of the User Clustering module.

>>>>

%The mapping between blog $B$ and user $U$ is a bilateral operation, i.e., $U = O(B)$ and $B \in B_s(U)$, through ID(s) of user and blog respectively.
Note that $M_b.O$ is a user, and $B_u$ is a set of $M_b$.

@@

\subsection{\sys{} Framework}
System \sys{} is designed from the ground up as a system for modeling users' \retg{} behavior in social media, and 
Figure \ref{fig:framework} shows the architectural components of \sys{}. %, mainly comprising Sina Microblog Data, Key Modules and Profile Demonstrator.

@@

	\stab(1)  Feature Extraction: By coalescing the microblog data, each user is depicted by a bunch of features, which are grouped into three categories. They are features of \textit{Basics} (e.g., the number of followers and followees), \textit{Behavior} (e.g., the frequency and the popular slots of \retg{}) and \textit{Interest} (e.g., long and short term interests, as well as explicit and implicit interests). These features are extracted from the stored  Sina Weibo data by Feature Extraction module, and serve as the input of the User Clustering module.
